Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-10-12 paper/main.tex
Added acronyms-package and more text to the tahoe-chapter

\usepackage{appendix} % Fixes formatting of appendices
\usepackage{graphicx} % We *may* use images
\usepackage{hyperref} % Internal and external links is nice
\hypersetup{pdfborder=0 0 0} % ..especially without red borders

@@

% Insert acronyms here

@@

\section{Tahoe-LAFS}
%What is it, how/where are hash functions used, Python, pycryptopp
%comparison with RAID-6

The Tahoe Least-Authority Filesystem is a system for secure,
distributed data storage \cite{t_tahoe}. Tahoe was originally developed with
funding from the former web backup service provider Allmydata, but is now a
stand-alone Open Source project \cite{t_ars}.

New files saved using Tahoe follow this pattern:
\begin{enumerate}
\item The file is encrypted using AES.
\item The file is split up into \emph{N} parts using \emph{erasure coding}.
\item The parts are distributed to \emph{N} storage servers.
\end{enumerate}

The use of erasure coding enables Tahoe to recover a file using only a
predefined subset of the parts distributed to the storage servers.

@@

\subsection{Advantages using a secure, distributed file system}
% Use cases?

@@

>>>>

\usepackage{appendix} % Fixes formatting of appendices
\usepackage[printonlyused]{acronym} % Package to handle the acronym list
\usepackage{graphicx} % We *may* use images
\graphicspath{{images/}} % and it is clean to put them in a separate dir
\usepackage{hyperref} % Internal and external links is nice
\hypersetup{pdfborder=0 0 0} % ..especially without red borders

@@

\begin{acronym}
\acro{AES}{Advanced Encryption Standard}
\acro{LAFS}{Least-Authority Filesystem}
\acro{FEC}{Forward Error Correction}
\end{acronym}

@@

Paralellizing

\section{Tahoe-LAFS}
%What is it, how/where are hash functions used, Python, pycryptopp
%comparison with RAID-6, mutable/immutable?

The Tahoe \ac{LAFS} is a system for secure,
distributed data storage. Files are encrypted client side, then
split up, before each part is sent to other nodes in the grid. The integrity and
confidentiality of the files are guaranteed by the algorithms used on the
client, and is independent of the storage servers, which may be operated by
untrusted people. This is defined as \emph{provider-independent security}
\cite{t_tahoe}.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{Tahoe-newfile.pdf}
    \caption{Tahoe-LAFS: Insertion of new file}
    \label{fig:tahoeinsertion}
\end{figure}

Tahoe was originally developed with funding from the former commercial web
backup service provider Allmydata, but is now a stand-alone Open
Source\footnote{GNU General Public License (GPL) version 2} project \cite{t_ars}.
It is written in the Python programming language with the Twisted framework, and
can run on Windows, Mac OSX, Linux, Solaris and more.

\subsection{Erasure coding}

The use of \emph{erasure coding} enables Tahoe to recover a file using only a
predefined subset of the parts distributed to the storage servers, i.e. the
other nodes in the grid. Erasure coding is a type of \ac{FEC} code, which
extends a message with $C$ characters into a longer message with $N$ symbols.
The original $C$ characters can then be recovered from a subset of the $N$
symbols.

@@

\subsection{Use of secure hashes in Tahoe-LAFS}

Where?

@@

Error sources.
